Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-08-03 chap-intro.tex
Clarify authorship of text to comply with regulations
Given the emphasis in regulations on who exactly wrote what, this seems
important.

\Cref{part:ch-aosd13} is based on work by \citet*{GiarrussoAOSD13}. While the
work was in collaboration, a few clearer responsibilities arose.
I did most of the implementation work, and collaborated to the writing: among
other things I devised the embedding for collection operations, implemented
optimizations and indexing, implemented compilation when interpretation did not
achieve sufficient performance, and performed the performance evaluation.
Michael Eichberg and Ralf Mitschke contributed to the evaluation by adapting
FindBugs queries.
Christian K{\"{a}}stner contributed, among other things, to the experiment
design for the performance evaluation. Klaus Ostermann proposed the original
idea (together with an initial prototype) and supervised the project.

The first chapters of \cref{part:incr} are originally based on work by \citet*{CaiEtAl2014ILC}, though
significantly revised; only \cref{sec:applying,sec:rw} survive mostly unchanged.
This work was even more of a team effort. I initiated and led the
overall project and came up with the original notion of change structures. Cai
Yufei contributed differentiation itself and its first correctness proof.
Tillmann Rendel contributed significant simplifications and started the overall
mechanization effort. Klaus Ostermann provided senior supervision that proved
essential to the project.
\Cref{part:incr} contains a novel correctness proof for simply-typed $\lambda$-calculus;
for its history and contributions \cref{sec:ilc-dev-history}.

>>>>

\Cref{part:ch-aosd13} is based on work by \citet*{GiarrussoAOSD13}, and
\cref{ch:aosd13-intro,ch:aosd13-solution,ch:aosd13-implementation,ch:aosd13-evaluation,ch:aosd13-relwork,ch:aosd13-concl}
come from that manuscript. While the
work was in collaboration, a few clearer responsibilities arose.
I did most of the implementation work, and collaborated to the writing: among
other things I devised the embedding for collection operations, implemented
optimizations and indexing, implemented compilation when interpretation did not
achieve sufficient performance, and performed the performance evaluation.
Michael Eichberg and Ralf Mitschke contributed to the evaluation by adapting
FindBugs queries.
Christian K{\"{a}}stner contributed, among other things, to the experiment
design for the performance evaluation. Klaus Ostermann proposed the original
idea (together with an initial prototype) and supervised the project.

The first chapters of \cref{part:incr} are originally based on work by
\citet*{CaiEtAl2014ILC}, though significantly revised;
\cref{ch:static-diff-intro} contains significantly revised text from that paper,
and \cref{sec:applying,sec:rw} survive mostly unchanged.
This work was even more of a team effort. I initiated and led the
overall project and came up with the original notion of change structures. Cai
Yufei contributed differentiation itself and its first correctness proof.
Tillmann Rendel contributed significant simplifications and started the overall
mechanization effort. Klaus Ostermann provided senior supervision that proved
essential to the project.
\Cref{ch:derive-formally,ch:change-theory} contain a novel correctness proof for
simply-typed $\lambda$-calculus; for its history and contributions see
\cref{sec:ilc-dev-history}.
